\bf Title

### 2024-02-23 article/paper_padic_spec.tex
modif in annuli

\subsection{Annuli (couronnes)}
\begin{definition}
	Annulus

	We call \emph{annulus} a set $A$ defined as $C = \{x \in K  | a\le \val(x) \le b\} $ for $a < b$ two nonnegative real numbers.
\end{definition}

\begin{theorem}
Annuli are spectrahedral shadows.
\end{theorem}

\begin{proof}
Let $A$ be the annulus defined by $a<b \in \R^*_+$. We consider for all $x,y \in K $ the spectrahedron $\mathcal{S}= \left\{(x,y) \in K  : M(x,y) := \pi^ax \oplus \pi^{-b}y \oplus \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix} \succeq 0\right\}$.

We will show that $x \in A$ if and only if  there exists $y\in K$ such that $(x,y) \in \mathcal{S}$.

Let $x,y \in K$. By \ref{caracsdp}, $M(x,y)$ is positive semidefinite if and only if $(x,y)$ is a solution of \ref{eq:annulussyst}.

\begin{equation}
  \label[type]{eq:annulussyst}
\begin{cases}
  \val(\pi^ax) \ge 0 \\
  \val(\pi^{-b}y) \ge 0\\
  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
  \val(\pi^{-2}\left( xy-1 \right))  \ge 0 
\end{cases}
\iff	
\begin{cases} 
		\val\left(x\right)\ge a\\
		\val\left(y\right)\ge -b\\
		\val\left( xy-1 \right) \ge 2
	\end{cases}
\end{equation}

Therefore, if $(x, y)$ verifies \ref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$. The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$. 
Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \ref{eq:annulussyst} .
\end{proof}

>>>>

\subsection{Annuli}

$\R^*_+$ denotes the set of positive real numbers.

\begin{definition}[Annulus]\label{def_annuli}
  A set of the form $A = \{x \in K \,|\, a \le \val(x) \le b\}$ for $a,b \in \R^*_+$ is called \emph{annulus}.
\end{definition}

\begin{theorem}
Annuli are spectrahedral shadows.
\end{theorem} 
\begin{proof}
  Let $A$ be as in \Cref{def_annuli}, for some $a,b \in \R^*_+$, assume $a<b$. Consider the spectrahedron
  $\mathcal{S} \subset K^2$ defined by
  $$
  \mathcal{S}= \left\{(x,y) \in K^2 : M(x,y) := \diag\left(\pi^ax, \pi^{-b}y, \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix}\right) \succeq 0\right\}.
  $$
We will show that $x \in A$ if and only if  there exists $y\in K$ such that $(x,y) \in \mathcal{S}$.
Let $x,y \in K$. By \Cref{caracsdp}, $M(x,y) \succeq 0$ if and only if $(x,y)$ is a solution of
\eqref{eq:annulussyst}:
\begin{equation}
  \label[type]{eq:annulussyst}
\begin{cases}
  \val(\pi^ax) \ge 0 \\
  \val(\pi^{-b}y) \ge 0\\
  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
  \val(\pi^{-2}\left( xy-1 \right))  \ge 0 
\end{cases}
\iff	
\begin{cases} 
		\val\left(x\right)\ge a\\
		\val\left(y\right)\ge -b\\
		\val\left( xy-1 \right) \ge 2
	\end{cases}
\end{equation}
Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$. The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$. 
Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \eqref{eq:annulussyst}.
\end{proof}
